---
title: "Step 01B MACS2 Call Candidate Regions"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

This notebook is a walk through of describing 1B of the steps in the ABC Enhancer Gene Prediction model

[broadinstitute/ABC-Enhancer-Gene-Prediction: Cell type specific enhancer-gene predictions using ABC model (Fulco, Nasser et al, Nature Genetics 2019)](https://github.com/broadinstitute/ABC-Enhancer-Gene-Prediction)  

We are wrapping the call candidate regions step.  The example code in the github repo is as follows

```
python src/makeCandidateRegions.py \
--narrowPeak example_chr22/ABC_output/Peaks/wgEncodeUwDnaseK562AlnRep1.chr22.macs2_peaks.narrowPeak.sorted \
--bam example_chr22/input_data/Chromatin/wgEncodeUwDnaseK562AlnRep1.chr22.bam \
--outDir example_chr22/ABC_output/Peaks/ \
--chrom_sizes example_chr22/reference/chr22 \
--regions_blocklist reference/wgEncodeHg19ConsensusSignalArtifactRegions.bed \
--regions_includelist example_chr22/reference/RefSeqCurated.170308.bed.CollapsedGeneBounds.TSS500bp.chr22.bed \
--peakExtendFromSummit 250 \
--nStrongestPeaks 3000 

```

## Shell script is used in the tool  

Notice the inline javascript such as ```$(inputs.bam.nameroot)```

```{bash, engine.opts='-l', echo=FALSE}
cat abc_enhancer_gene_prediction/step01B_macs2_call_candidate_regions/files/make_candidate_regions.sh
```


## Rcwl code

```{r Rcwl, eval=FALSE, message=FALSE}
library(Rcwl)
library(tidyverse)

#input ports
input_ports = list(
InputParam(id = "narrow_peak", type = "File"),
InputParam(id = "bam", type = "File", 
           secondaryFiles = list(pattern = ".bai"), value = list("BAM")),
InputParam(id = "chr_sizes", type = "File"),
InputParam(id = "regions_blocklist", type = "File"),
InputParam(id = "regions_includelist", type = "File")
)

#output ports
output_ports = list(
OutputParam(id = "candidate_regions", type = "File", 
            glob = '*candidateRegions.bed'),
OutputParam(id = "counts", type = "File", 
            glob = '*Counts.bed')
)

#requirements
docker = "images.sb.biodatacatalyst.nhlbi.nih.gov/andrewblair/cardiac-compendium:2023042401"
shell_script = Dirent(entryname = "make_candidate_regions.sh", read_file("make_candidate_regions.sh"), writable = FALSE)

#hints
hints = list(class = "sbg:SaveLogs", value = "*.sh")

make_candidate_regions <- cwlProcess(
  label: MACS2 Call Candidate Regions
  baseCommand = list("bash", "make_candidate_regions.sh"),
  inputs = do.call(InputParamList, c(input_ports)),
  outputs = do.call(OutputParamList, c(output_ports)),
  requirements = list(
    requireDocker(docker), 
    requireJS(),
    requireShellCommand(),
    requireInitialWorkDir(list(shell_script))),
  hints = list(hints))

#write cwl to file
writeCWL(make_candidate_regions, outdir = "./")

```

## Push to a Seven Bridges platform

Note: this could be a good spot to inject some additional SB specific yaml tags.

```{r eval=FALSE}

system("~/.local/bin/sbpack bdc dave/abc-development-scratch-project/")
system("rm make_candidate_regions.yml")

```

